\Large \bf \projtitle

### 2015-05-05 doc/paper/paper.tex
Add download manager related sections

% Anish

@@

% Anish

@@

% Anish

>>>>

When fetching content peer-to-peer, it is necessary to authenticate data that
is downloaded. \zbf\ achieves this by using a cryptographic hash function to
authenticate data that is downloaded. Assets that are to be downloaded
peer-to-peer are identified by their hash, and once the download manager
finishes downloading the content from peers, it verifies that the hash of the
contents matches what is expected. The download manager rejects content if
there is an authentication error. In the current implementation, if this
occurs, the download manager falls back to downloading the content over HTTP
from the fallback URL.

@@

\zbf\ divides assets into chunks primarily to enable parallelization. Because
individual peers may not have high outbound bandwidth, it is beneficial to
download in parallel from many peers. Our implementation parallelizes chunk
downloads, with pending chunk requests balanced between available peers in the
network. If certain peers are slow to respond, the download manager
automatically requests chunks from faster peers to optimize download time.
Parallel downloads help reduce download latency.

@@

Our download manager implements reliable download semantics. The implementation
is resilient to peer failure, automatically re-requesting chunks from live
peers when necessary. In the worst case, even if all peers go down, the
implementation falls back to downloading over pure HTTP from the centralized
server as a last resort. In any case, the download manager guarantees that the
data will be downloaded and that the download will be authenticated.
